\documentclass{article}
\usepackage[left=0.75in,top=0.8in,right=0.75in,bottom=0.6in]{geometry} 
\usepackage{hyperref} 
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{array}% for extended column definitions    

\sectionfont{\fontsize{10}{52}\selectfont}

\begin{document}

\begin{center}
\textbf{\huge HENOK WEHIBE} \\
\vspace{1.5em}
\href{mailto:henokwehibe@gmail.com}{henokwehibe@gmail.com} \\
\vspace{1.0em}
\href{https://linkedin.com/in/henokwehibe}{https://linkedin.com/in/henokwehibe}\\
\vspace{1.0em}
\href{https://github.com/micrometre}{https://github.com/micrometre }\\
\end{center}
\vspace{-4.6em}
\section* {WORK EXPERINCE}
\vspace{0.6em}
\hrule 
{\bf}{} MicrometeUK \hfill {} \\% Bold company name and date on the right
{\em Lead/Full stack developer} \hfill {\em 2022 - 2024 } % Italic job title and location

As a key contributor, I led the development of an Automatic Number Plate Recognition (ANPR) system as a service. 
This project successfully automated the manual data entry of number plate presence  eliminating human error.
Furthermore, I spearheaded the migration of on-premises servers to the AWS cloud, 
leveraging EC2 instances for compute and  S3 for storage resulting in a substantial reduction in infrastructure costs.



\begin{enumerate}
    \item[] Designed a Python/Flask backend with Redis and a React frontend. 
   \begin{itemize}
    \item Integrated the React frontend with  Python/Flask backend using RESTful APIs.
    \item Developed a  user interface with React, enhancing user experience and responsiveness.
   \end{itemize}
\end{enumerate}


\begin{enumerate}
    \item[] Developed Ansible roles to automate deployment across multiple environments.
   \begin{itemize}
    \item Automated the deployment of the React frontend and Python/Flask backend using Ansible roles, enabling continuous integration and delivery.
    \item Eliminated manual configuration errors and ensured consistent deployments across all environments.  
    \item Increased system reliability and reduced downtime through automated configuration management with Ansible.
   \end{itemize}
\end{enumerate}

\begin{enumerate}
    \item[]  Leveraged Redis with SSE(Server-Sent Events) to provide instant updates without the need for constant
    \begin{itemize}
    \item Implemented a Redis Pub/Sub channel to broadcast parking activity updates from the backend.
    \item Developed an SSE endpoint in the Python/Flask backend to push updates to connected clients.
    \item integrated client-side JavaScript/React  to handle incoming SSE events and update the user interface dynamically.
    \end{itemize}
 \end{enumerate}


\begin{enumerate}
    \item[] Utilized pandas to clean and process ANPR data,  removing duplicates, correcting errors, and standardizing formats for subsequent analysis
   \begin{itemize}
    \item Improved the accuracy of ANPR data analysis by  cleaning and processing the data with pandas. 
    \item Facilitated data sharing  by exporting processed ANPR data to CSV, Excel, and JSON formats using pandas.
   \end{itemize}
\end{enumerate}


\begin{enumerate}
    \item[]  Developed cross-platform desktop applications with Electron and mobile apps with Ionic Framework, seamlessly
   \begin{itemize}
    \item Utilized RESTful APIs to enable communication between the Electron/Ionic apps and the Flask backend, facilitating real-time data exchange and ANPR functionality.
    \item Leveraged Electron and Ionic to create native apps for multiple platforms (Android), expanding the reach of the ANPR service and increasing user accessibility.
   \end{itemize}
\end{enumerate}


\begin{enumerate}
    \item[] Built a low-power SoC IoT camera using an Arduino ESP32, integrating a camera module for video
   \begin{itemize}
    \item Designed the hardware and firmware for a SoC IoT camera using an ESP32 microcontroller, integrating a camera module for video capture and Wi-Fi for network connectivity.
    \item Leveraged the ESP32's built-in Wi-Fi capabilities to enable wireless video streaming. 
    \item Integrated the camera with a cloud platform for remote access, live streaming, and storage of video footage
   \end{itemize}
\end{enumerate}



\begin{enumerate}
    \item[] Integrated real-time video streaming using FFmpeg and OpenCV into the ANPR system, enabling continuous monitoring and analysis of vehicle traffic.
   \begin{itemize}
    \item Utilized FFmpeg and OpenCV to create a video streaming pipeline that feeds live footage into the ANPR system for immediate number plate recognition
    \item Leveraged FFmpeg to efficiently encode and stream video data from the ESP32 camera to the ANPR system, minimizing latency and bandwidth consumption
   \end{itemize}
\end{enumerate}




\vspace{1.4em}
\hrule 
\vspace{0.4em}
\hspace{-2.em}
{\bf}Freelance/Self Employed  \hfill {} \\% Bold company name and date on the right
{\em Web Developer } \hfill {\em 2020 - 2022 } % Italic job title and location
\subsection*{}
\vspace{-2.6em}

\begin{enumerate}
    \item[] Developed e-commerce websites, landing pages, and blogs for clients across various industries leveraging WordPress and React.
   \begin{itemize}
    \item Provided a comprehensive suite of services, including domain registration, email hosting, website design and development, and ongoing website maintenance.
    \item Offered custom website solutions tailored to clients' needs, from initial concept and design to development, deployment, and search engine optimization.
    \item Improved website loading speeds  by utilizing Edge Computing Hosting and optimizing website performance.
    \item Performed comprehensive website audits encompassing performance, accessibility, best practices, and SEO, utilizing tools like Google Lighthouse.
    \item Implemented features like store locators, custom map markers, and dynamic zoom levels using the Google Maps API within the WordPress theme.
   \end{itemize}
\end{enumerate}



\vspace{1.4em}
\hrule 
\vspace{0.4em}
\hspace{-2.em}
{\em Projects } \hfill {\em 2020 - 2022 } % Italic job title and location


\begin{enumerate}
    \item Customized Debian/Linux distributions to create specialized versions for desktops, laptops, and servers, including pre-installed software  and custom branding
   \begin{itemize}
    \item Utilized remastering tools and scripts to create customized Debian/Linux distributions.
    \item Manually configured and optimized Debian/Linux distributions to meet specific performance and security requirements for desktops, laptops, and servers.
    \item Built custom images using Packer to create consistent and reproducible development and testing environments, eliminating configuration inconsistencies.
    \item Configured KVM, QEMU, and Vagrant on host machines to create a versatile virtualization environment for running multiple VMs, enabling efficient development, testing, and deployment of applications
    \item Hosted and maintained Gitea instances on cloud platforms (AWS, Azure, GCP) for private source code management, ensuring high availability, security, and performance
    \item Established a private Docker Registry to securely store and manage Docker images for internal projects, ensuring controlled access and efficient distribution
    \item Implemented Nginx as a reverse proxy to handle incoming requests, caching static content, and routing traffic to appropriate backend servers.
    \item Enabled SSL termination with HAProxy and Nginx to secure web traffic and protect sensitive data.
    \item Developed an Ansible role that automates the installation and configuration of WireGuard, enabling rapid and secure deployment of VPN servers and clients.
    \item Implemented Fail2ban to protect critical services (SSH, WordPress, Gitea) from brute-force attacks.
    \item Integrated Monit, Crontab, and Git to create a comprehensive monitoring system.\\
     Monit actively monitors system resources and services.\\
     crontab schedules regular checks.  \\
     Git tracks configuration changes for auditing and rollback capabilities.
    \item Installed and set up Kubernetes clusters using kubeadm and Microk8s for deploying and managing containerized applications.\\
    Configured network plugins Calico and Flannel to enable communication between pods and services within the Kubernetes cluster. \\
    Deployed Nginx Ingress Controller on Kubernetes and configured it with Let's Encrypt certificates using Cert-Manager, enabling secure HTTPS access to applications\\
    Reduced Docker image build times and cost by implementing a private registry. 
   \end{itemize}
\end{enumerate}


\section* {TECHNICAL TOOLS AND SOFTWARE}
\hrule 
\subsection*{}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{5ex}} l }
Configuration management & Ansible\\
Container orchestration & Kubernetes\\
Cloud Technologies & AWS, GCP and Azure \\
Languages& Python and Javascript \\
Databases & MySql, Redis and Monogodb \\
Version Control & Git\\
Testing Framework & Cypress 
\end{tabular}
   
\vspace{1.4em}
\section* {CERTIFICATIONS}
\hrule 
\subsection*{}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{9ex}} l l }
 FreeCodeCamp & Responsive Web Design  \\
 FreeCodeCamp & JavaScript Algorithms and Data Structures \\
\end{tabular}
\vspace{1.4em}
\section* {EDUCATION}
\hrule 
\vspace{0.4em}
{\em South Thames College} \hfill {\em 1993 - 1997  } \\% Italic job title and location
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{5ex}} l }
Diploma & Information technology \\
GCSE  & Triple Science in Biology, Chemistry, and Physics \\
GCSE  & English, and Maths \\
\end{tabular}



\end{document}

