\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Henok Wehibe} % Your name
\address{London UK} 
\address{henokwehibe@gmail.com}
\address{https://github.com/micrometre}

\begin{document}


\begin{rSection}{Work Experience}
\begin{rSubsection}{MicrometeUK}{2022 -  2024}{Lead/Full stack developer}

\item Led the development of an Automatic Number Plate Recognition (ANPR) as a service project, encompassing  cloud infrastructure, image processing, API design, and  user interface development.
\item Created Ansible roles to automate the deployment of the ANPR Parking Management application across multiple environments.
\item Leveraged Redis  with SSE(Server-Sent Events) to provide instant updates without  the need for constant page refreshes.
\item Integrated real-time video streaming using FFmpeg and OpenCV into the ANPR system, enabling continuous monitoring and analysis of vehicle traffic.
\item Used pandas to clean and preprocess ANPR data, ensuring accuracy and consistency for subsequent analysis.
\item Developed a new user interface with React, enhancing user experience and responsiveness.
\item Integrated the React frontend with the Python/Flask backend using RESTful APIs.
\item Developed cross-platform desktop applications with Electron and mobile apps with Ionic, seamlessly integrating them with the ANPR Flask backend
\item Built a low-power SoC IoT camera using an  Arduino ESP32, integrating a camera module for video capture and transmission to the ANPR system
\end{rSubsection}
\begin{rSubsection}{Freelance/Self Employed}{2022 - 2023}{Web Devloper }{}
\item Developed e-commerce websites, landing pages, and blogs for clients across various industries, leveraging my expertise in  WordPress and React.
\item Provided a comprehensive suite of services, including domain registration, email hosting, website design and development, and ongoing website maintenance.
\item Offered custom website solutions tailored to clients' needs, from initial concept and design to development, deployment, and search engine optimization.
\item Improved website loading speeds  by utilizing Edge Computing Hosting and optimizing website performance.

\end{rSubsection}
\end{rSection}

\begin{rSection}{Project}
\begin{rSubsection}{Home Laboratory }{2017 - 2022}{}
\item Remastering Ubuntu/Linux distributions to install on desktops laptops and
servers, Building custom images using Packer, Vagrant for development and
testing environment.
\item Configured KVM, Virtualbox, Proxmox and LXD for host machines to run
multiple virtual machines (VMs).
\item Utilizing HAProxy and Nginx for reverse proxy, load balancer, and SSL Termination.
\item Creating custom wordpress themes.
\item Setting up Private Docker Registry  to reduce build times.  
\item Installation and setting up kubernetes cluster with kubeadm and Mikrok8s. 
\item Hosting and maintaining Gitea for private Source Code Management.
\item Construction and configuration of local Servers with remote administration.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Technical Tools and Software}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Configuration management & Ansible\\
Container orchestration & Kubernetes\\
Cloud Technologies & AWS and Azure \\
Languages& Python, Javascript and Shell scripting\\
Databases & MySql, Redis and Monogodb \\
Version Control & Git\\
\end{tabular}
\end{rSection}


\begin{rSection}{Certifications}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
freeCodeCamp  & Javascript\\
NodeSchool & Node.js\\
\end{tabular}
\end{rSection}

\begin{rSection}{Education}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
South Thames College &  Diploma, Information Technology \\
\end{tabular}
\end{rSection}
\end{document}
